Computational Six-bar Synthesis for Implementing Dynamic Behavior

### 2019-02-03 draft.tex
Version submitted for review.  Abstract & keywords modified to comply with IEEE submission rules.

\author{Mark~M.~Plecnik %,~\IEEEmembership{Member,~IEEE,}
        and~Ronald~S.~Fearing,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
\thanks{M.~Plecnik is with the Department of Aerospace and Mechanical Engineering, University of Notre Dame, IN, 46556 USA e-mail: {\tt\small plecnikmark@nd.edu}}% <-this % stops a space
\thanks{R.~S.~Fearing is with the Department of Electrical Engineering and Computer
Sciences, University of California, Berkeley, CA 94720 USA e-mail: {\tt\small ronf@eecs.berkeley.edu}}% <-this % stops a space
\thanks{Manuscript received February xx, 2019; revised Month xx, 2019.}}

@@

\begin{abstract}
Designing a robotic mechanism to perform some desired dynamic behavior under limited actuation power is a challenge.
Descriptions of dynamic requirements inherently exist in the time domain while extant mechanism synthesis techniques are predominantly geometric in nature.
To bridge this gap, we consider the dynamics of a simplified ``mock-up'' model of a motor acting through a spring and mechanism to push an inertia.
This model excludes the mechanism's dimensions and topology in place of user-defined mechanism characteristics.
The characteristics that produce desired dynamic behavior serve as a goal for a to-be-designed mechanism discovered during subsequent kinematic synthesis.
Following this, the synthesis method employed must be capable of sufficiently matching user-defined nonlinearities.
Linkages of the six-bar topology provide this capability but are challenged with design equations of very high degree that have not been solved before.
In this work, we solve one such system of design equations using the Finite Root Generation technique.
Our approach is motivated by an application for small legged robots to increase power density through kinematic design rather than actuator sizing.
While not possible for a directly driven mechanism, we show how this is done using series-elastic actuation.
We design leg mechanisms capable of continuously recycling a foot path while producing locomotive power within a single stride beyond its actuator's limit.
Candidate designs are presented that are capable of producing 3.0 times the actuator's power in simulation.
Experimental results of one such mechanism demonstrated a decrease from the ideal down to 2.6 times the actuator's power.
\end{abstract}

\begin{IEEEkeywords}
Mechanism dynamics, kinematic synthesis, robot design
\end{IEEEkeywords}

@@

We have presented a method for designing the dynamic behavior of a loaded mechanism.
First, we analyzed a simplified model of our proposed system in order to discover the mechanism characteristics that would result in the desired dynamics.
The model was run according to user-defined mechanism characteristics in the absence of a mechanism design.
Instead, these characteristics serve as a design goal for a to-be-designed mechanism found during a subsequent kinematic synthesis step.
The prescribed characteristics included a single degree-of-freedom point path and a coordinated mechanical advantage profile.
Kinematic synthesis was executed to discover six-bar linkages that exhibit the desired mechanism characteristics.
These characteristics were encoded into design constraints resulting in a highly nonlinear system of design equations.
This system of equations was solved for the first time in this paper using the Finite Root Generation technique.
The generation of a nearly complete solution set of such a large system allows an exploration of the design space to be conducted.
We applied our methodology to the design of a leg mechanism for a small running robot powered by a series-elastic actuator.
The leg mechanism is capable of propelling itself forward at powers beyond its motor's limit while recycling foot position during every stride with the motor only rotating in the forward direction.
A few linkage design solutions were presented, one of which was built and tested.
In simulation, it achieved a propulsive power 3.0 times its motor's limit.  In experiment, propulsive power was 2.6 times its motor's limit.

>>>>

\author{Mark~M.~Plecnik %,~\IEEEmembership{Member,~IEEE,}
        and~Ronald~S.~Fearing,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
\thanks{M.~Plecnik is with the Department of Aerospace and Mechanical Engineering, University of Notre Dame, IN, 46556 USA e-mail: {\tt\small plecnikmark@nd.edu}}% <-this % stops a space
\thanks{R.~S.~Fearing is with the Department of Electrical Engineering and Computer
Sciences, University of California, Berkeley, CA 94720 USA e-mail: {\tt\small ronf@eecs.berkeley.edu}}% <-this % stops a space
\thanks{Manuscript received February 3, 2019; revised Month xx, 2019.}}

@@

\begin{abstract}
Designing a robotic mechanism to perform some desired dynamic behavior under limited actuation power is a challenge.
Descriptions of dynamic requirements inherently exist in the time domain while extant mechanism synthesis techniques are predominantly geometric in nature.
To bridge this gap, we consider the dynamics of a simplified ``mock-up'' model
%of a motor acting through a spring and mechanism to push an inertia.
that excludes mechanism dimensions and topology in place of user-defined kinematic characteristics.
The characteristics that produce the desired dynamic behavior serve as a goal for a to-be-designed mechanism discovered during subsequent kinematic synthesis.
Following this, the synthesis method employed must be capable of sufficiently matching user-defined nonlinearities.
Linkages of the six-bar topology provide this capability but are challenged with design equations of very high degree that have not been solved before.
We solve these equations using the Finite Root Generation technique.
%Our approach is motivated by an application for small legged robots to increase power density through kinematic design rather than actuator sizing.
%While not possible for a directly driven mechanism, we show how this is done using series-elastic actuation.
Our approach is motivated by an application for small legged robots to find a leg mechanism powered by a series elastic actuator capable of recycling a foot path while producing locomotive power within a single stride beyond the actuator's limit.
%While not possible for a directly driven mechanism, we show how this is done using series-elastic actuation.
%We design leg mechanisms capable of continuously recycling a foot path while producing locomotive power within a single stride beyond its actuator's limit.
%Candidate designs are presented that are capable of producing 3.0 times the actuator's power in simulation.
%Experimental results of one such mechanism demonstrated a decrease from the ideal down to 2.6 times the actuator's power.
\end{abstract}

\begin{IEEEkeywords}
%Mechanism dynamics, kinematic synthesis, robot design, homotopy continuation
Mechanism design, computational geometry, dynamics, kinematics
\end{IEEEkeywords}

@@

We have presented a method for designing the dynamic behavior of a loaded mechanism.
First, we analyzed a simplified model of our proposed system in order to discover the kinematic characteristics that would result in the desired dynamics.
The model was run according to user-defined kinematic characteristics in the absence of a mechanism design.
Instead, these characteristics serve as a design goal for a to\nobreakdash-be\nobreakdash-designed mechanism found during a subsequent kinematic synthesis step.
The prescribed characteristics included a single degree\nobreakdash-of\nobreakdash-freedom point path and a coordinated mechanical advantage profile.
Kinematic synthesis was executed to discover six-bar linkages that exhibit the desired mechanism characteristics.
These characteristics were encoded into design constraints resulting in a highly nonlinear system of design equations.
This system of equations was solved for the first time in this paper using the Finite Root Generation technique.
The generation of a nearly complete solution set of such a large system allows an exploration of the design space to be conducted.
We applied our methodology to the design of a leg mechanism for a small running robot powered by a series-elastic actuator.
The leg mechanism is capable of propelling itself forward at powers beyond its motor's limit while recycling foot position during every stride with the motor only rotating in the forward direction.
A few linkage design solutions were presented, one of which was built and tested.
In simulation, it achieved a propulsive power 3.0 times its motor's limit.  In experiment, propulsive power was 2.6 times its motor's limit.
